\documentclass[11pt, oneside]{article}  
\usepackage{geometry}  
% \usepackage{nunito}
\usepackage{cmbright}
\geometry{letterpaper}   
\usepackage{cite}
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex	
\usepackage{tcolorbox}
\usepackage{amssymb}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{url}
\usepackage{color}
\definecolor{c1}{rgb}{0.12, 0.56, 1.0}
%SetFonts
\usepackage{xspace}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{authblk} 

\definecolor{fruitpushorange}{RGB}{255, 127, 0}

\usepackage{soul}
\DeclareRobustCommand{\cms}[1]{ {\begingroup\sethlcolor{fruitpushorange}\hl{(cms:) #1}\endgroup} }
%SetFonts


\title{Data-driven imputation of compound miscibility via matrix factorization with graph regularization}
\author[1]{Diba Behnoudfar}
\author[1,$\dagger$]{Cory M. Simon}
\author[2,*]{Joshua Schrier}
\affil[1]{School of Chemical, Biological, and Environmental Engineering. Oregon State University. Corvallis, OR. USA. }
\affil[2]{Department of Chemistry, Fordham University, The Bronx, New York 10458, USA}
\affil[$\dagger$]{\texttt{cory.simon@oregonstate.edu}} 
\affil[*]{\texttt{jschrier@fordham.edu}}

%\affil[*]{}
\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle

\begin{abstract}

\end{abstract}

\section{Introduction}

\cite{shu2022robust}

\section{Problem setup: imputing compound miscibility, leveraging compound features}

\section{Graph-regularized matrix factorization for imputing compound miscibility}

\subsection{The data}
data: $\{ m_{ij} \}_{(i, j) \in \Omega_{\text{obs}}}$ where $m_{ij}\in\{0, 1\}$ is the miscibility of compound $i$ and $j$ (0: immiscible, 1: miscible).
The set $\Omega_\text{obs} \subset \{1,..n\} \times \{1, ..., n\}$ is the set of observed tuples.

\subsection{The miscibility model}
$c_i \in \mathbb{R}^k$: latent vector representation of compound $i$.

model
\begin{equation}
	m_{ij} \approx \sigma(c_i \cdot c_j + b)
\end{equation}

\subsection{Training}

loss:

\begin{multline}
	\ell(C, b) = - \displaystyle \sum_{(i, j) \in \Omega_{\text{obs}}} \left[ m_{ij} \log \left(\sigma(c_i \cdot c_j+b)\right) + (1-m_{ij}) \log \left(1-\sigma(c_i \cdot c_j+b)\right)  \right] \\
	+ \lambda \displaystyle\sum_{i=1}^n \lvert \lvert c_i \rvert \rvert^2 + \gamma  \displaystyle \sum_{(i, j)} k(i, j) \lvert \lvert c_i - c_j \rvert \rvert^2
\end{multline}

gradients

\begin{equation*}
     \nabla_{\vec{c_i}}\ell = -\sum_{(i,j) \in \Omega} \vec{c_j} (\hat{m}_{ij} -m_{ij}) +  2\gamma \sum_{(i,j)} K(i,j)( \vec{c_i} - \vec{c_j}) + 2\lambda \sum_{i} \vec{c_i} \\
\end{equation*}

\begin{equation*}
     \nabla_b\ell = -\sum_{(i,j) \in \Omega}  (\hat{m}_{ij} -m_{ij})  \\
\end{equation*}


\subsection{Hyperparameter tuning}
parameters: 
\begin{itemize}	
	\item latent compound vectors, $C$
	\item bias, $b$
\end{itemize}
hyperparameters:
\begin{itemize}	
	\item dimension of latent space, $k$ 
	\item compound vector regularization param, $\lambda$
	\item graph-regularization param, $\gamma$
	\item (if features) the bandwidth of the kernel parameter
\end{itemize}


\section{Results}

\subsection{Simulating incomplete experiments to generate incomplete miscibility matrix}

\subsection{A typical outcome}
\subsubsection{The pairwise compound miscibility matrix}

\subsubsection{Training and hyper-parameter tuning}

\subsubsection{The latent space of compounds}
\subsubsection{Miscibility imputation performance}

\subsubsection{Comparisons: with, without graph regularization}
  \begin{itemize}
   \item vanilla matrix factorization ($\gamma=0$) vs.\ graph-regularized matrix factorization $\gamma > 0$.
   \item class-only $k(i,j)$ vs.\ feature-vector-based $k(i, j)$. okay both are features. just combine?
  \end{itemize}


\subsection{Ensemble of performances, over different sparsities}

\subsection{Baseline models}

not comparable to paper b/c theirs is complete.

train RF on obs data. predict on unobs data.

idea 1: train one RF per compound. 

idea 2: train RF, input = concat two compound features, then data augmentation to impose permutation invariance. need to do class weights to handle their resampling. 

random baseline (guessing), with proportion in training data.

\section{convo with Joshua, Dec 19}
kernels that can handle missing data?

scan hyperparams: (a) keep $\lambda$, $k$ set same, randomly selected or (b) scan grid.

if we generate enuff numbers, then ok...

p-value/hypothesis test. for random choice of hyper-params. which model does better?

Joshua likes class-only. then don't need to find the features and do imputation. 




uncertainty quantification via bootstrap?

\bibliography{refs}
\bibliographystyle{unsrt}

\end{document}  
